Uniformly Ergodic Data-Augmented MCMC for Fitting Stochastic Epidemic Models to Incidence Data

### 2021-10-15 Manuscripts/Article/Article.tex
Updates from Overleaf

@@

	Figure \ref{fig:traceplot} shows the traceplots of the parameters $\beta$ and $\gamma$, the log likelihood and the basic reproduction number $R_0 = S(0) \beta / \gamma$, which corresponds to the average number of secondary infections generated by an infectious individual in a susceptible population. We observe that the Markov chain quickly migrates from the low density region of the space where $(\beta^{(1)}, \gamma^{(1)})$ is located to a high density region where it mixes well. The acceptance rate of the latent spaces proposed in the Metropolis-Hastings step is $0.11$.
	Excluding the first $10,000$ iterations of the Markov chain as a burn-in, the posterior means of $\beta$, $\gamma$ and $R_0$ are respectively $0.00304$, $0.995$ and $3.07$.

@@

	\begin{figure}
		\centering
		\begin{subfigure}[b]{0.42\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E1_trajectories}
			\caption{Compartment trajectories}
			\label{fig:E1_trajectories}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.41\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E1_no_burn_gamma_tp}
			\caption{$\gamma$}
			\label{fig:traceplot_gamma}
		\end{subfigure}
		\\
		\begin{subfigure}[b]{0.41\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E1_no_burn_gamma_hist}
			\caption{Log likelihood}
			\label{fig:traceplot_loglik}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.41\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E1_burn_gamma_acf}
			\caption{$R_0$}
			\label{fig:traceplot_R0}
		\end{subfigure}
		\caption{Performance of the proposed DA-MCMC in a medium-sized population $(S(0), I(0)) = (1000, 10)$.}
		\label{fig:E1}
	\end{figure}

>>>>

	% the basic reproduction number $R_0 = S(0) \beta / \gamma$, which corresponds to the average number of secondary infections generated by an infectious individual in a susceptible population

@@

	Figure \ref{fig:E1_no_burn_gamma_tp} shows the traceplot of the parameter $\gamma$ among the first $10000$ iterations. We observe that the Markov chain quickly migrates from the low density region where it is initialized to the high density region where it mixes well. The acceptance rate of the latent spaces proposed in the Metropolis-Hastings step is $0.18$.

	Excluding the first $10,000$ iterations of the Markov chain as a burn-in, the posterior means of $\beta$, $\gamma$ and $R_0$ are respectively $0.00304$, $0.995$ and $3.07$.

@@

	\begin{figure}
		\centering
		\begin{subfigure}[b]{0.42\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E1_trajectories}
			\caption{Compartment trajectories}
			\label{fig:E1_trajectories}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.41\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E1_no_burn_gamma_tp}
			\caption{$\gamma$}
			\label{fig:E1_no_burn_gamma_tp}
		\end{subfigure}
		\\
		\begin{subfigure}[b]{0.41\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E1_no_burn_gamma_hist}
			\caption{Log likelihood}
			\label{fig:E1_no_burn_gamma_hist}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.41\textwidth}
			\centering
			\includegraphics[width=\textwidth]{E1_no_burn_gamma_acf}
			\caption{$R_0$}
			\label{fig:\textbf{traceplot_R0}}
		\end{subfigure}
		\caption{Performance of the proposed DA-MCMC in a medium-sized population $(S(0), I(0)) = (1000, 10)$.}
		\label{fig:E1}
	\end{figure}
